%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.1, 7 December 2016) written by LianTze Lim (liantze@gmail.com). 
%% Now compiles with both XeLaTeX and LuaLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}
\documentclass[10pt,a4paper]{altacv}

\input{../common/preamble.tex}
\usepackage{multicol}

\begin{document}

\input{../common/personal.tex}

%% Make the header extend all the way to the right, if you want. Extend the right margin by 8cm (=6.8cm marginparwidth + 1.2cm marginparsep)
\begin{adjustwidth}{}{-8cm}
\makecvheader
\end{adjustwidth}
\vspace{0.3cm}

%add color block
\begin{textblock}{10}(9.5,1.95)
  \centering
  \textblockcolour{VeryLightGrey}
	aaa
  \vspace{250mm}
\end{textblock}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.

\cvsection[viviani_cv-p1sidebar]{\printinfo{\faInstitution}{Education}}

\cvevent{M.Sc.\ in Theoretical physics}{University of Torino, 104/110}{2015}{Collegio Universitario ``R. Einaudi'', Torino}{
Scholarship winner: "Piano Lauree Scientifiche 2008", granted by Società Italiana di Fisica.}

\divider

\cvevent{Ph.D. in Computer Science}{University of Torino, Computer Science Dept.}{2015 -- 2019}{Torino, IT}{Thesis:
\textit{Deep Learning at Scale with Nearest Neighbours Communications}.\\Supervisor: Marco Aldinucci. Funded by Noesis Solutions.}
\smallskip

\divider

\cvaccentpar{Academic activity}
\begin{itemize}
  \item Several publications on peer-reviewed computer science proceedings
  \item Program committee member in several conferences
  \item Co-supervisor of one M.Sc. Thesis
\end{itemize}

\cvsection{\printinfo{\faIndustry}{Experience}}

\cvevent{Noesis Solutions}{Reasearch Engineer}{April 2015 -- Permanent}{Novara, IT}
\begin{itemize}
\item Development of machine learning modelling methodologies for engineering.
\item Development of high-performance numerical code.
\item Cloud and container technologies exploitation.
\item Supervision of one internship.
\item Re-designed internal source code management workflow.
\end{itemize}


\cvaccentpar{Funded research projects}
Technical contact for the following research projects. Including presentation to European Commission reviewers.
\smallskip
\begin{itemize}
  \item MACH -- ITEA2 project
\item Fortissimo 2 -- H2020-FoF project
\item CloudFlow -- FP7-I4MS project
\item Blockchain for online Service Security -- IMEC-ICON Flemish project
\item VaProFam -- FlandersMake-ICON Flemish project
\item DC-CDS -- FlandersMake-ICON Flemish project
\end{itemize}

\cvsection{\printinfo{\faPlane}{Free time}}
Avid traveller and photographer.\\
Former track \& field athlete, now turned to playground basketball.\\
\medskip
\faCamera \hspace{0.4pc} \url{paoloph.myportfolio.com}


\end{document}