%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.1, 7 December 2016) written by LianTze Lim (liantze@gmail.com). 
%% Now compiles with both XeLaTeX and LuaLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}
\documentclass[10pt,a4paper]{altacv}

\input{common/preamble.tex}

%% sample.bib contains your publications
\addbibresource{viviani_cv.bib}

\begin{document}

\input{common/personal.tex}

%% Make the header extend all the way to the right, if you want. Extend the right margin by 8cm (=6.8cm marginparwidth + 1.2cm marginparsep)
\begin{adjustwidth}{}{-8cm}
\makecvheader
\end{adjustwidth}

%add color block
\vspace{0.5cm}
\begin{textblock}{10}(9.5,2.1)
  \centering
  \textblockcolour{VeryLightGrey}
	aaa
  \vspace{250mm}
\end{textblock}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.

\cvsection[viviani_cv-p1sidebar]{\printinfo{\faUser}{Profile}}
I'm a theoretical physicist turned computer scientist with 5+ years of industrial research experience in the field of HPC and ML/DL.

\cvsection{\printinfo{\faInstitution}{Education}}

% \cveventlogo{unito_logo.pdf}
\cvevent{Ph.D., Computer Science}{University of Torino}{2015 -- 2019}{Torino, IT}{Thesis:
\textit{Deep Learning at Scale with Nearest Neighbours Communications}.\\Supervisor: Marco Aldinucci. Funded by Noesis Solutions.}
\smallskip

\divider

\cvevent{Master's Degree, Theoretical physics}{University of Torino, 104/110}{2015}{Collegio Universitario ``R. Einaudi'', Torino}{
Scholarship winner: "Piano Lauree Scientifiche 2008", granted by Società Italiana di Fisica.}
%https://web.archive.org/web/20200528081355/https://www.sif.it/attivita/lauree_scientifiche/vincitori2008

\cvsection{\printinfo{\faIndustry}{Experience}}

% \cveventlogo{links_logo.jpg}
\cvevent{LINKS Foundation}{Senior Researcher, Advanced Computing}{2021 -- present}{Torino, IT}
\smallskip
\begin{itemize}
\item \textbf{HPC, Machine Learning and Big Data convergence} -- acceleration of scientific/technical applications
\item \textbf{Quantum algorithms and applications} -- discrete optimization on neutral atoms machines and quantum annealers 
\item \textbf{ML/DL algorithms for neural signal decoding}
\item \textbf{Funded research projects} -- proposals writing, technical management and execution
\item ETP4HPC Working groups member
\end{itemize}

\divider

% \cveventlogo{noesis_logo.jpg}
\cvevent{Noesis Solutions}{Reasearch Engineer}{2015 -- 2021}{Novara, IT}
\begin{itemize}
\item \textbf{Machine learning methodologies for engineering modelling and design exploration}
\item Development of numerical code and software stack
\item Supervisor of one internship
\item Technical contact for funded research projects
\end{itemize}




%\divider
\clearpage

%add color block
\vspace{0.5cm}
\begin{textblock}{10}(9.5,0.5)
  \centering
  \textblockcolour{VeryLightGrey}
	aaa
  \vspace{278mm}
\end{textblock}
\cvsection[viviani_cv-p2sidebar]{\printinfo{\faBook}{Research Activity}}

\cvsubsection{Funded Research Projects}
See \href{http://paoloviviani.github.io/projects}{\color{accent}\textbf{paoloviviani.github.io/projects}} for full list and details.
\medskip

\cvproject{B-CRATOS}{H2020-FET Open}{2021 -- ongoing}
\cvproject{ACROSS}{H2020-EuroHPC}{2021 -- ongoing}
\cvproject{Lexis}{H2020-ICT-11}{2021 -- 2022}
\cvproject{BoSS}{IMEC-ICON}{2018 -- 2019}
\cvproject{Fortissimo 2}{H2020-FoF project}{2016 -- 2018}
\cvproject{CloudFlow}{FP7-I4MS project}{2016 -- 2017}
\cvproject{MACH}{ITEA2}{2015 -- 2016}
%\cvproject{DC-CDS}{FlandersMake-ICON}{2019 -- 2021}{

\divider

\renewcommand*{\bibfont}{\small}
\cvsubsection{Selected Publications}
See \href{https://paoloviviani.github.io/publications}{\color{accent}\textbf{paoloviviani.github.io/publications}} for full list.
\medskip
\medskip
\nocite{*}
\medskip
\printbibliography[heading=none]

\divider

\cvsubsection{Other}
\begin{itemize}
\item Co-supervisor of one M.Sc. Thesis
\item Over 35 conference and journal papers reviewed
\item Four PhD schools attended.
\item Program Committee member, \textit{Euromicro International Conference on Parallel, Distributed, and Network-based Processing (PDP)} for 2018 (also session chair), 2019 and 2020.
\item Program Committee member, \textit{Parallel Numerical Methods and Libraries for Heterogeneous Multi/Manycores (PDP2018 and PDP2019)}.
\item Program Committee member, \textit{Artifact Evaluation, Euro-Par 2018}
\item Program Committee member, \textit{16th IEEE International Conference on Scalable Computing and Communications (ScalCom 2016)}.
\end{itemize}


\end{document}
